Current and future constraints on primordial magnetic fields

### 2015-11-13 pmf.tex
intro v1

Magnetic fields are ubiquitous in astronomy and are found almost universally in collapsed objects from galaxies and galaxy clusters \citep[for review, see][]{ryu12, widrow12}. 
There is even some evidence for magnetic fields in intergalactic space from \fermilat{} data \citep{neronov10}, although alternative explanations \citep{broderick12} have been proposed. 
High energy $\gamma$-rays from blazars should  produce electron-positron pairs when the $\gamma$-rays collide with IR or optical photons. 
These pairs should later annihilate in at GeV energies, but the expected GeV flux is missing in the \fermilat{} observations. 
Intergalactic magnetic fields could explain the missing flux by deflecting the particles. 
If due to intergalactic magnetic fields, the GeV results set lower limits on the magnetic field strength of $10^{-9} - 10^{-6}$.\,nG \citep{tavecchio10,taylor11,dermer11,vovk12}.

@@

recent results

>>>>

Magnetic fields are ubiquitous in astronomy and are found almost universally in collapsed objects from galaxies and galaxy clusters \citep[for review, see][]{ryu12, widrow12}. 
There is even some evidence for magnetic fields in intergalactic space from \fermilat{} data \citep{neronov10}, although alternative explanations \citep{broderick12} have been proposed. 
High energy $\gamma$-rays from blazars should  produce electron-positron pairs when the $\gamma$-rays collide with IR or optical photons. 
These pairs should later annihilate in at GeV energies, but the expected GeV flux is missing in the \fermilat{} observations. 
Intergalactic magnetic fields could explain the missing flux by deflecting the particles. 
If due to intergalactic magnetic fields, the GeV results set lower limits on the magnetic field strength of $10^{-9} - 10^{-6}$\,nG \citep{tavecchio10,taylor11,dermer11,vovk12}.

@@

Primordial magnetic fields would have observational consequences for Big Bang nucleosynthesis \citep[e..,][]{kahniashvili10}, large scale structure \citep[e.g.,][]{battaner97}, the black body spectrum of the CMB \citep[e.g.,][]{kunze14}, as well as the CMB anisotropy. 
The CMB anisotropies have yielded some of the strongest constraints on PMFs and are the focus of this work.
There have been two recent results of note. 
\citet{planck15-19} have used the \planck{} 2015 release of temperature and polarization data to set limits on a variety of PMF models. 
With the CMB power spectrum data that will be the focus of this paper, \citet{planck15-19} find 95\% CL upper limits ranging from $\bpmf < 5.6$\,nG to $<0.7$\,nG depending on the exact model. 
The \pb{} collaboration also recently announced limits on PMFs from the \pb{} data using either a 4-point estimator or B-mode power spectrum measurement in \citep{pb}. 
The strongest constraints were from the B-mode spectrum; the observed upper limit was $\bpmf < \tbd{4.0}$\,nG. 
Two other experiments, \sptpol{} and \bicepkeck{}, have reported B-mode power spectrum measurements recently \citep{}.
In this paper, we will combine the data from all four experiments to determine simple limits on the PMF, and then examine Fisher matrix forecasts on PMF models from the stage-III and stage-IV CMB experiments being built or designed right now.
